---
title: "rcocolors User Guide"
author: "Brian Froeb"
date: "7/27/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r echo=FALSE}
library(ggplot2)
library(tmap)
library(rcocolors)
data(NLD_muni)
```

There are currently 16 colors included in this package the color names and their hex codes are below
```{r, echo=FALSE}
rco_color_list
```

These are grouped into 6 color palettes, 3 diverging color palettes and 3 single color ramps. The colors included in each palette and their hex codes are below
```{r, echo=FALSE}
rco_color_palettes
```

These color palettes can be inserted into ggplot graphics, examples of each palettes in ggplot are below

## Functions Included

This package includes four functions:

-rco_cols()
-rco_color_pal()
-scale_color_rco()
-scale_fill_rco()

#### rco_cols
takes a input string or group of strings and returns the hex code. 
The color must be one of the colors included in this package

##### Example:
```{r}
rco_cols("blue1")

rco_cols("teal1", "brown3")
```

#### rco_color_pal

Converts an input string representing a color palette into a function that can be converted into a usable color palette.

```{r}
rco_color_pal("blue to orange")
```

By adding a step count after the function it will return a usable palette

```{r}
rco_color_pal("blue to orange")(10)
```

These palettes can be reversed as needed

```{r}
rco_color_pal("blue to orange", reverse = TRUE)(10)
```

#### scale_color_rco and scale_fill_rco

These functions supply a fill or color to a ggplot call. 

